Polka-dotted Stars: a Hierarchical Model for Mapping Stellar Surfaces Using Occultation Light Curves and the Case of TOI-3884

### 2025-02-27 src/tex/ms.tex
static

While we cannot definitively determine whether the spot is in the northern or southern hemisphere based on the transit data alone, 
the presence of either configuration would lead to similar physical interpretations regarding the underlying stellar dynamo processes. 
This latitude distribution, combined with the other spot parameters discussed previously, presents compelling evidence for strong, 
organized magnetic fields concentrated at the rotational poles of TOI-3884.

\begin{figure*}[hbt!]
    \centering
    \includegraphics[width=\textwidth]{figures/toi3884-active-lats.pdf}
    \caption{Posterior probability distribution of spot latitudes for TOI-3884. The black line shows the mean distribution, 
    while the pink lines represent individual posterior samples from our MCMC analysis. The distribution peaks at high latitudes 
    ($\pm75^{\circ}$) with minimal probability near the equator, indicating a strong preference for near-polar spots.
    The symmetry across 
    the equator reflects the inherent degeneracy in determining the hemisphere of spot locations from transit data alone.}
    \label{fig:spot_latitudes}
\end{figure*}

@@

We find a planetary radius of $R_p = 0.188 \pm 3\times10^{-3}$ $R_\earth$ and an orbital period of 
$P_\text{orb} = 4.5446^{+2.7\times10^{-5}}_{-2.4\times10^{-5}}$ days.

\begin{table}[]
    \vspace{0.5cm}
    \centering
    \caption{The free parameters for TOI-3884 data in Section \ref{sec:toi3884}, their true values, and their priors.}
    \begin{tabular}{llll}
    \hline
    Parameter                                 & Inferred value    \\ \hline\hline
    $i_p (^\circ)$                                     & $90.17^{+0.52}_{-0.78}$                   \\
    $e$                                       & $0.14^{+0.19}_{-0.07}$                     \\
    $P (\rm days)$                                       & $4.5446^{+2.7\times10^{-5}}_{-2.4\times10^{-5}}$                       \\
    $t_0 (\rm days)$                                     & $2556.51\pm 4\times 10^{-4}$                       \\
    $R_p / R_\star$                           & $0.188 \pm 3\times10^{-3}$                         \\ 
    $u_1$                                     & $0.14^{+0.15}_{-0.07}$                         \\ 
    $u_2$                                     & $0.09 \pm 0.06$                         \\ 
    $v\sin i (\rm kms^{-1})$                                & $1.69^{+0.11}_{-0.09}$                       \\ \hline
    $i_\star (^\circ)$                                 & $34.8^{+5.62}_{-6.17}$                      \\
    $\lambda_\star (^\circ)$                           & $80.37^{+49.6}_{-27.5}$                           \\
    $P_\star (\rm days)$                                 & $9.07^{+0.45}_{-0.51}$                       \\ 
    $\rho_\star (\rm gcm^{-3})$                              & $15.18^{+1.98}_{-1.75}$                      \\ \hline
    $\mathbb{r} (^\circ)$                              & $26.77^{+9.7}_{-8.7}$                           \\
    $\mathbb{c}$                              & $0.049^{+0.028}_{-0.013}$                               \\
    $\mathbb{n}$                              & $7.58^{+1.39}_{-2.85}$                               \\
    $\mu_\phi (^\circ)$                                & $75.24^{+2.67}_{-4.11}$                               \\
    $\sigma^2_\phi (^\circ)$                           & $12.99^{+4.91}_{-5.08}$                      \\ \hline
    \label{tab:ResultsT0i3884}
    \end{tabular}
\end{table}
%

>>>>

While we cannot definitively determine whether the spot is in the northern or southern hemisphere based on the transit data alone, 
the presence of either configuration would lead to similar physical interpretations regarding the underlying stellar dynamo processes. 
This latitude distribution, combined with the other spot parameters discussed previously, presents compelling evidence for strong, 
organized magnetic fields concentrated at the rotational poles of TOI-3884.
%
\begin{figure*}[hbt!]
    \centering
    \includegraphics[width=\textwidth]{figures/toi3884-active-lats.pdf}
    \caption{Posterior probability distribution of spot latitudes for TOI-3884. The black line shows the mean distribution, 
    while the pink lines represent individual posterior samples from our MCMC analysis. The distribution peaks at high latitudes 
    ($\pm75^{\circ}$) with minimal probability near the equator, indicating a strong preference for near-polar spots.
    The symmetry across 
    the equator reflects the inherent degeneracy in determining the hemisphere of spot locations from transit data alone.}
    \label{fig:spot_latitudes}
\end{figure*}
%

@@

We find a planetary radius of $R_p = 0.188 \pm 3\times10^{-3}$ $R_\star$ and an orbital period of 
$P_\text{orb} = 4.5446^{+2.7\times10^{-5}}_{-2.4\times10^{-5}}$ days.

\begin{table}[]
    \vspace{0.5cm}
    \centering
    \caption{The free parameters for TOI-3884 data in Section \ref{sec:toi3884}, their true values, and their priors.}
    \begin{tabular}{llll}
    \hline
    Parameter                                 & Inferred value    \\ \hline\hline
    $i_p (^\circ)$                                     & $90.17^{+0.52}_{-0.78}$                   \\
    $e$                                       & $0.14^{+0.19}_{-0.07}$                     \\
    $P (\rm days)$                                       & $4.5446^{+2.7\times10^{-5}}_{-2.4\times10^{-5}}$                       \\
    $t_0 (\rm days)$                                     & $2556.51\pm 4\times 10^{-4}$                       \\
    $R_p / R_\star$                           & $0.188 \pm 3\times10^{-3}$                         \\ 
    $u_1$                                     & $0.14^{+0.15}_{-0.07}$                         \\ 
    $u_2$                                     & $0.09 \pm 0.06$                         \\ 
    $v\sin i (\rm kms^{-1})$                                & $1.69^{+0.11}_{-0.09}$                       \\ \hline
    $i_\star (^\circ)$                                 & $34.8^{+5.62}_{-6.17}$                      \\
    $\lambda_\star (^\circ)$                           & $80.37^{+49.6}_{-27.5}$                           \\
    $P_\star (\rm days)$                                 & $9.07^{+0.45}_{-0.51}$                       \\ 
    $\rho_\star (\rm gcm^{-3})$                              & $15.18^{+1.98}_{-1.75}$                      \\ \hline
    $\mathbb{r} (^\circ)$                              & $26.77^{+9.7}_{-8.7}$                           \\
    $\mathbb{c}$                              & $0.049^{+0.028}_{-0.013}$                               \\
    $\mathbb{n}$                              & $7.58^{+1.39}_{-2.85}$                               \\
    $\mu_\phi (^\circ)$                                & $75.24^{+2.67}_{-4.11}$                               \\
    $\sigma^2_\phi (^\circ)$                           & $12.99^{+4.91}_{-5.08}$                      \\ \hline
    \label{tab:ResultsT0i3884}
    \end{tabular}
\end{table}
%
Figure \ref{fig:toi3884-transits} presents the transit light curves of TOI-3884 from eight separate transit events. 
Each panel shows the phase-folded photometric data (gray points with error bars) along with the results from our model. 
The solid pink lines represent the model average from 100 posterior samples, while the light pink shaded regions indicate the 
$1\sigma$ uncertainty bounds of our model. The x-axis shows time in days relative to the mid-transit point 
(indicated by the offset values), and the y-axis displays the normalized flux.

These transit light curves reveal several notable features. The slight asymmetry visible in the transit profiles provides strong 
evidence for the stellar surface inhomogeneities due to spot-crossings. In particular, the subtle variations between different 
transit epochs (particularly visible in transits 3, 4, and 8) are consistent with the high-latitude spot configuration we've 
identified. Our model successfully captures the essential features of all eight transit events, including the ingress and egress 
shapes as well as the in-transit variations. The quality of the fit across multiple epochs demonstrates the robustness of 
our spot model and stellar orientation constraints. The consistency between the observed data and our model supports our conclusion 
that TOI-3884 hosts a significant near-polar spot that influences the transit morphology across multiple planetary orbits.

%
\begin{figure*}[hbt!]
    \centering
    \includegraphics[width=\textwidth]{figures/toi3884-model-transits.pdf}
    \caption{Light curves for eight transit events of TOI-3884b. Each panel shows the observed photometric data from TESS (gray points 
    with error bars) and the results of our MCMC modeling. The solid pink lines represent the model average from 100 posterior 
    samples, while the light pink shaded regions indicate the 1$\sigma$ uncertainty bounds. The x-axis displays time in days 
    relative to the mid-transit point (shown as offsets at the bottom of each panel), and the y-axis shows the normalized flux. 
    The slight asymmetries and variations between transit epochs are consistent with the influence of a high-latitude stellar spot. 
    Our model successfully reproduces the observed transit profiles across all epochs, supporting our inferred spot and stellar 
    orientation parameters.}
    \label{fig:toi3884-transits}
\end{figure*}
%
